Choose a License

### 2024-09-18 choose_license.qmd
Fix typo
Provide more details for TL;DR

Every expression of an idea, such as literary or artistic works, are automatically covered by copyright. This means that nobody else than the copyright holder is allowed to copy, modify, or share it. Copyright licenses can grant others some of the necessary rights, but mostly don't cover publicity, privacy, moral, patent, or trademark rights.

@@

1. Recording the copyright notices and licenses for files by others (for example, in a file called `LICENSE.txt`) and following all their additional requirements.
2. In the simplest case, choosing two licenses (one for code, one for everything else) which to apply  simultaneously (at the choice of the recipient) to all own files (for example, again by recording the license in the file `LICENSE.txt`).

@@

> The Quarto files in this project are made available under CC\ BY-SA\ 4.0, or (at your option) under the terms of the Apache Software License\ 2.0.

>>>>

Every expression of an idea, such as a literary or an artistic works, is automatically covered by copyright. This means that nobody else than the copyright holder is allowed to copy, modify, or share it. Copyright licenses can grant others some of the necessary rights, but mostly don't cover publicity, privacy, moral, patent, or trademark rights.

@@

1. Recording the copyright notices and licenses for files by others (for example, in a file called `LICENSE.txt`) and following all their additional requirements.
2. In the simplest case, choosing two licenses (one for code, one for everything else) which to apply  simultaneously to all own files (for example, again by recording the license in the file `LICENSE.txt`). Recipients are then free to choose under which of the two licenses to use the material.

We recommend to choose [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/) and [Apache\ 2.0](https://choosealicense.com/licenses/apache-2.0/) for all own works. Take your time to read the summaries behind the links and/or the actual license text to understand its legal effect.

You can adapt the following wording to your use case:

> Except otherwise noted, all files in this project are made available under CC0\ 1.0 or (at your option) under the terms of the Apache Software License\ 2.0.

@@

> The Quarto files in this project are made available under CC0\ 1.0 or (at your option) under the terms of the Apache Software License\ 2.0.
